BERT Model Compression and Weight Sharing

### 2019-05-12 paper/paper.tex
Fix misc typos
Add KD discussion

\begin{table}[tbh]
        \caption{Results for Knowledge Distillation}
        \label{tab:kd_results}
        \centering
        \vspace{1em}
        \begin{tabular}{lccccccc}
\toprule
{} &  framework &  type &  val loss &  ß val acc \\
{} & \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\
\midrule
0 &        nokd &   CNN &   $0.906$ &   $0.799$ \\
1 &        nokd &   CNN &   $0.448$ &   $0.784$ \\
2 &        nokd &   CNN &   $0.856$ &   $0.812$ \\
3 &          kd &  LSTM &   $0.738$ &   $0.831$ \\
4 &          kd &   CNN &   $0.423$ &   $0.834$ \\
\bottomrule
\end{tabular}

\end{table}

\section{Discussion}
Things to say about deeptwist
\begin{itemize}
  \item Stratified prune better
  \item Prune rate mad robust
  \item Diff gud
  \item ``Improved performance''
  \item QQP takes long, but looks okay
  \item Didn't try only purning the $\bert$ part
\end{itemize}

Things to say about KD
\begin{itemize}
  \item it bad
  \item doens't work
  \item LSTM weird/CNN incrdibly noisy
  \item \TODO{compare}
\end{itemize}

>>>>

\begin{table}[tbh]
        \caption{Results for Knowledge Distillation}
        \label{tab:kd_results}
        \centering
        \vspace{1em}
        \begin{tabular}{lccccccc}
\toprule
{} &  framework &  type &  val loss &  ß val acc \\
{} & \hypertarget{tabcol:1}{(1)} & \hypertarget{tabcol:2}{(2)} & \hypertarget{tabcol:3}{(3)} & \hypertarget{tabcol:4}{(4)} \\
\midrule
0 &        nokd &   CNN &   $0.906$ &   $0.799$ \\
1 &        nokd &   CNN &   $0.448$ &   $0.784$ \\
2 &        nokd &   CNN &   $0.856$ &   $0.812$ \\
3 &          kd &  LSTM &   $0.738$ &   $0.831$ \\
4 &          kd &   CNN &   $0.423$ &   $0.834$ \\
\bottomrule
\end{tabular}
\label{tbl:kdresults}
\end{table}

\section{Discussion}

Things to say about DeepTwist
\begin{itemize}
  \item Stratified prune better
  \item Prune rate mad robust
  \item Diff gud
  \item ``Improved performance''
  \item QQP takes long, but looks okay
  \item Didn't try only pruning the $\bert$ part
\end{itemize}

Things to say about KD
\begin{itemize}
  \item it bad
  \item doesn't work
  \item LSTM weird/CNN incredibly noisy
  \item \TODO{compare}
\end{itemize}

When compared to the performance of a fine-tuned BERT on SST-2, our Knowledge
Distillation results---displayed in \cref{tbl:kdresults}---fall short. However,
it is important to note the student networks are also much smaller than BERT. To
isolate the effect of KD, we compare the performance of
\citet{kim2014convolutional}'s CNN trained on the correct labels versus the BERT
probabilities. This suggests a modest performance benefit of two percentage
points in validation accuracy. However, we see no evidence of training being
sped up by using KD.

We also identify some curious behavior in the KD training curves. When training
the LSTM on the BERT outputs, neither training loss nor validation loss decrease
at first. In fact, they stay approximately constant for a couple of epochs. Only
after this prolonged period does loss abruptly start going down, producing a
normal curve from that point forward. We find this remarkably puzzling. We
hypothesize this may be the effect of our adaptive learning rate starting out
too low and taking multiple epochs to grow to a point where it can meaningfully
update parameters. 
% TODO: include this graph -- screenshot from tensorboard?
